Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-06-16 paper/paper.tex
draft edits

	Lastly, the governing equation for temperature in the molten salt is given
	as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q,
	\label{eq3}
\end{align}
%
	where
{\small
\begin{align}
	\rho &= \text{density of molten salt} \\
	 c_{p} &= \text{specific heat capacity of molten salt} \\
	 T &= \text{temperature of molten salt} \\
	 \overrightarrow{u} &= \text{velocity of molten salt} \\
	 k &= \text{thermal conductivity of molten salt},
\end{align}
	and the source term $Q$ is given as:
%
\begin{align}
Q = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}

@@

@@

\begin{figure}[H] 
	\centering
	\includegraphics[width=.48\textwidth]{./figures/totalflux}
	\captionsetup{justification=centering}
	\caption{Total radial neutron flux at reactor half-height, for start-up,
	\gls{BOL}, and equilibrium fuel compositions at steady state.}
	\label{fig:totalflux}
\end{figure}

\begin{figure}[H] 
	\centering
	\includegraphics[width=.48\textwidth]{./figures/stflux}
	\captionsetup{justification=centering}
	\caption{Total radial neutron flux at reactor half-height, for start-up,
	\gls{BOL}, and equilibrium fuel compositions at steady state.}
	\label{fig:stflux}
\end{figure}

\begin{figure*}%
\centering
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/sttemp}%
\end{subfigure}\hfill%
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/eltemp}%
\end{subfigure}\hfill\\
\bigskip
\centering
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/eqtemp}%
\label{subfigc}%
\end{subfigure}%
\captionsetup{justification=centering}
\caption{Temperature distributions within the fuel salt region, for start-up
(top left), \gls{BOL} (top right), and equilibrium (bottom) fuel compositions at steady state. The height and radius are in the Y and X directions
respectively.}
\label{fig:temp}
\end{figure*}

\section{Unprotected Loss of Flow}

	An unprotected loss of flow accident may occur due to pump failure. In such
	a scenario, a slower circulation loop is set up through natural convection.
	Previous studies have shown that the pumps coast down
	exponentially with a time constant to a velocity approximately 18 times
	slower \cite{fiorina_modelling_2014}.

@@

>>>>

	Lastly, the governing equation for temperature in the molten salt is given
	as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q,
	\label{eq3}
\end{align}
%
	where
{\small
\begin{align}
	\rho &= \text{density of molten salt} \\
	 c_{p} &= \text{specific heat capacity of molten salt} \\
	 T &= \text{temperature of molten salt} \\
	 \overrightarrow{u} &= \text{velocity of molten salt} \\
	 k &= \text{thermal conductivity of molten salt},
\end{align}
}
	and the source term $Q$ is given as:
%
\begin{align}
Q = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}

@@

\begin{figure*}%
\centering
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/sttemp}%
\end{subfigure}\hfill%
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/eltemp}%
\end{subfigure}\hfill\\
\bigskip
\centering
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/eqtemp}%
\label{subfigc}%
\end{subfigure}%
\captionsetup{justification=centering}
\caption{Temperature distributions within the fuel salt region, for start-up
(top left), \gls{BOL} (top right), and equilibrium (bottom) fuel compositions at steady state. The height and radius are in the Y and X directions
respectively.}
\label{fig:temp}
\end{figure*}
%
\begin{figure}[H] 
	\centering
	\includegraphics[width=.53\textwidth]{./figures/totalflux}
	\captionsetup{justification=centering}
	\caption{Total radial neutron flux at reactor half-height, for start-up,
	\gls{BOL}, and equilibrium fuel compositions at steady state.}
	\label{fig:totalflux}
\end{figure} 
\begin{figure}[H] 
	\centering
	\includegraphics[width=.53\textwidth]{./figures/stflux}
	\captionsetup{justification=centering}
	\caption{Neutron group fluxes at reactor half-height, for start-up
	fuel composition at steady state.}
	\label{fig:stflux}
\end{figure}

@@

	Total power as defined by Eq. \ref{eq4} is approximately 2 GW. This
	is 1 GW less than the rated 3 GW of the \gls{MSFR}. This may be mainly due
	to the erroneous uniform velocity profile imposed in the core. From
	fluid dynamics, velocity along the central axis of the core should be
	higher than the velocity at the periphral areas near the blanket tank.
	The higher velocity at the center results in higher advective heat transfer
	away from the center of the core and cools the active region. This should
	result in an increase in neutron flux from the strongly negative
	temperature reactivity feedback, and thus higher heat generation. The
	truncation of the top and bottom fuel salt region is also a factor for
	the lower than expected heat production.

	Comparing the three different fuel compositions, the \gls{MSFR} operates at
	the highest temperatures with the start-up fuel composition, followed by
	the \gls{BOL}, and the equilibrium compositions. This may be due to the
	generation of $^{233}$Pa as an intermediate for $^{233}$U breeding as
	mentioned by Rykhlevskii et al. (cite Andrei) in their fuel cycle analysis
	of the \gls{MSFR}.

\section{Loss of Secondary Cooling Accident}

	A \gls{LOSCA} may occur due to various causes of failure in the secondary
	coolant loop such as secondary loop pump failure or loss of secondary
	coolant. While it is less likely in an \gls{MSFR} as it consists of 16
	separate coolant loops each with its own secondary cooling system, the
	potential consequences must still be studied.
	The loss of secondary cooling is simulated by exponentially decreasing
	the heat loss rate in the Moltres heat exchanger kernel with a time
	constant of 5 s.

	The loss of heat sink is expected to cause an initial temperature spike,
	followed by a decrease in neutron flux and heat generation due to the
	strongly negative temperature reactivity feedback. Eventually, the
	\gls{MSFR} should settle on a new steady state with a higher average
	temperature than the operating temperature. If the high temperature is
	sustained for a long period of time, it could lead to severe damage
	in the reactor, pipes, or other instruments.

\begin{figure}[b] 
	\centering
	\includegraphics[width=.53\textwidth]{./figures/loscatemp}
	\captionsetup{justification=centering}
	\caption{Average core fuel temperature for start-up, \gls{BOL}, and
	equilibrium fuel compositions during \gls{LOSCA}.}
	\label{fig:loscatemp}
\end{figure} 
%
\begin{figure}[t] 
	\centering
	\includegraphics[width=.53\textwidth]{./figures/loscaheat}
	\captionsetup{justification=centering}
	\caption{Total thermal power generated, for start-up, \gls{BOL}, and
	 equilibrium fuel compositions during \gls{LOSCA}.}
	\label{fig:loscaheat}
\end{figure}

	As observed in Figure \ref{fig:loscatemp}, the average fuel temperature
	increased by approximately 10 K and reached the new steady state
	30-40 s after \gls{LOSCA} began. While the time delay, due to the high
	initial
	\gls{DNP} concentration, is in good agreement with results reported by
	Fiorina et al. \cite{fiorina_modelling_2014}, the temperature rise is much
	smaller than the 100 K increase reported by the same authors.
	Power generation fell by two orders of
	magnitude, resulting in a negligible temperature difference between the
	inlets and outlets for all three fuel compositions. This could also be
	attributed to the relatively small total power of 2 GW discussed in the
	previous section, and the truncated \gls{MSFR} model.

	In comparing the three fuel compositions, a \gls{MSFR} loaded with
	start-up fuel composition is at a higher risk as it has higher
	temperatures under normal operating conditions and accident scenarios.

@@

	Summarise results

	Safe

	Further development of the models is necessary to improve the accuracy
	and reliability of Moltres as a coupled neutronics/thermal-hydraulics code.
	Further work includes using an arbitrarily defined velocity profile, such
	as a parabolic profile. A better option would be to
